Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-31 main_paper.tex
[#26] update rdrobust citations
Closes #26

The paper is organized as follows. Section~\ref{background} describes the basic
RD approach, its usual implementation, and the explicit analytical bias
correction approach in the literature. Section~\ref{boot} presents our proposed
bootstrap bias corrected RD algorithm and discusses its asymptotic
properties. Simulation evidence that the bootstrap procedure provides valid CIs
and its relative performance to the analytical bias correction are presented in
Section~\ref{sim} and Section~\ref{application} demonstrates the estimator's
usage by applying it to the Head Start dataset used
by~\cite{ludwig2007}.\footnote{%
  The simulations and empirical analysis were carried out in the R programming
  language \citep{R} and rely on the \textit{rdrobust} \citep{rdrobust},
  \textit{doParallel}, \textit{foreach} \citep{doparallel,foreach}, and
  \textit{doRNG} \citep{dorng} packages. Our source code is available online
  at \url{https://github.com/grayclhn/boot-rd}.} %
Finally, Section~\ref{conclusion} concludes.

>>>>

The paper is organized as follows. Section~\ref{background} describes the basic
RD approach, its usual implementation, and the explicit analytical bias
correction approach in the literature. Section~\ref{boot} presents our proposed
bootstrap bias corrected RD algorithm and discusses its asymptotic
properties. Simulation evidence that the bootstrap procedure provides valid CIs
and its relative performance to the analytical bias correction are presented in
Section~\ref{sim} and Section~\ref{application} demonstrates the estimator's
usage by applying it to the Head Start dataset used
by~\cite{ludwig2007}.\footnote{%
  The simulations and empirical analysis were carried out in the R programming
  language \citep{R} and rely on the \textit{rdrobust}
  \citep{rdrobust2,rdrobust3},
  \textit{doParallel}, \textit{foreach} \citep{doparallel,foreach}, and
  \textit{doRNG} \citep{dorng} packages. Our source code is available online
  at \url{https://github.com/grayclhn/boot-rd}.} %
Finally, Section~\ref{conclusion} concludes.
